\Large \bf FlexAlloc: Dynamic Memory Partitioning\\ between the Corevisor and Hostvisor in SeKVM

### 2023-12-24 paper.tex
formatting issues

We evaluate FlexAlloc by running it on a QEMU-emulated Raspberry Pi 4. In
particular, we run VMWare Fusion Professional Version 13.0.2 on an M1 Macbook
Air running MacOS Ventura 13.6. Using VMWare, we create a VM
with 2 processor cores and 8704 MB memory running Ubuntu 22.04.3 LTS. On this
VM, we run QEMU 6.2.0 to emulate a Raspberry Pi 4. This emulated Raspberry
Pi 4 serves as our host machine, on which we run FlexAlloc. Our guest VMs
run vanilla Linux v5.4.

@@

@@

One key shortcoming of FlexAlloc is that it is not formally verified. In
this sense, FlexAlloc is less like SeKVM and more like HypSec. It provides isolation guarantees
in principle, but cannot be logically proven to be secure. In particular, there
are a few major flaws in FlexAlloc when it comes to isolating guest VMs from
the host machine. For instance, the current implementation of FlexAlloc
does not use \textit{memset} to zero out the memory given to it by the hostvisor
for the VM's stage-2 page table. This presents a danger if the MMU tries to
read from a page table entry that should not actually exist, but that has
previously been written into the memory region by the hostvisor. Another flaw is that
FlexAlloc does not verify that the eight 1M regions are actually distinct and
do not overlap with one another. Hence, FlexAlloc still fundamentally relies on
a non-malicious hostvisor, and would require further patches to be fully secure.

>>>>

We evaluate FlexAlloc by running it on a QEMU-emulated Raspberry Pi 4. In
particular, we run VMWare Fusion Professional Version 13.0.0 on a 2018 x86-64 Macbook
Pro running MacOS Ventura 13.6.1. Using VMWare, we create a VM
with 4 processor cores and 12 GB memory running Ubuntu 22.04.3 LTS. On this
VM, we run QEMU 6.2.0 to emulate a Raspberry Pi 4. This emulated Raspberry
Pi 4 serves as our host machine, on which we run an SeKVM with the FlexAlloc
extension. Our guest VMs run vanilla Linux v5.4.

@@

In order to make sure that the host can reasonably be expected to find 8x 1MB
contiguous regions when booting a VM, we evaluated how many successful
alloc_pages(1MB) calls could be made before failure. To reproduce our tests,
simply compile host-sekvm-project with the \textit{ALLOC\_STRESS\_TEST} macro defined.
Across our three trails, after booting host SeKVM with the FlexAlloc extension,
we were able to achieve between 7049 and 7054 successful 1MB allocations
from alloc_pages(1MB) calls. Since each VM only needs 8 successful allocations,
we believe that the upperbound on the number of VM's due to potential alloc_pages(1MB)
failures is sufficiently high.

We verified the changes in corevisor's memory footprint by checking the number of
pages owned by the corevisor according to the \textit{el2\_data\-\>s2\_pages} array at key points
throughout the VM boot and destruction processes. On a host running SeKVM without the
FlexAlloc extension, we observed that the Corevisor owned 65549 pages before booting a VM,
while running a VM, and after destroying a VM. On a host running SeKVM with the FlexAlloc
extension, we observed that the Corevisor owned 32768 pages before VM boot, 34817 pages
during the life of the VM, and 32768 pages after destroying the VM. Note that FlexAlloc also
reduces the static stage2_region size in the linker script to zero as it is no longer needed.
These findings show that FlexAlloc is able to successfully receive, use, and handback pages
given by the host for usage exclusively as VM stage-2 page tables.

@@

One key shortcoming of FlexAlloc is that it is not formally verified. In
this sense, FlexAlloc is less like SeKVM and more like HypSec. It provides isolation guarantees
in principle, but cannot be logically proven to be secure. In particular, there
are a few major flaws in FlexAlloc when it comes to isolating guest VMs from
the host machine. For instance, the current implementation of FlexAlloc
does not use \textit{memset} to zero out the memory given to it by the hostvisor
for the VM's stage-2 page table. This presents a danger if the MMU tries to
read from a page table entry that should not actually exist, but that has
previously been written into the memory region by the hostvisor. We also occasionally
observed stalls when booting subsequent VMs after shutting down other VMs that we
believe were caused by failing to \textit{memset} the pages to zero. For example, the second
VM to boot after booting and shutting down the first VM can receive pages with non-zero data
that, when interpretted as page table entries, lead to undefined behavior.

Another flaw is that
FlexAlloc does not verify that the eight 1M regions are actually distinct and
do not overlap with one another. Hence, FlexAlloc still fundamentally relies on
a non-malicious hostvisor, and would require further patches to be fully secure.
To fix this, FlexAlloc can simply have an added check that verifies all of the
physical addresses received from the host are unique, 1MB aligned, and non-overlapping.
